Pillar 1 - Student Topic Profile

### 2019-04-16 Pillar 1 - Topic Profile.Rmd

course_target <- course_current[! str_detect(course_current, "...10..")] 
course_target <- setdiff(course_target, "CAP3000") # exclude capstone
course_target <- union(course_target, str_subset(course_current, "COR"))# include core courses
```

@@

# Preparation

@@

  left_join(gamma, by = "topic") %>%
  rename(preparation = document) %>%
  filter(target != preparation) %>%

  # exclude 3000 (advanced) courses from preparation courses
  filter(!preparation %>% str_detect("^...30")) %>%

  # double prep_score of intro courses
  mutate(is_intro = preparation %>% str_detect("^...10")) %>%
  mutate(weight = weight * (1 + is_intro)) %>%

@@

  # aggregate prep_score
  group_by(target, preparation) %>%
  summarize(prep_score = sum(prep_score)) %>%

>>>>

course_target <- course_current[! str_detect(course_current, "...10..")]
course_target <- union(course_target, str_subset(course_current, "COR"))# include core courses
```

@@

# Preparatory courses

@@

  left_join(gamma, by = "topic") %>%
  rename(`Preparatory Courses` = document) %>%
  filter(target != `Preparatory Courses`) %>%

  # exclude 3000 (advanced) courses from preparation courses
  filter(! `Preparatory Courses` %>% str_detect("^...30")) %>%

  # double prep_score of intro courses
  mutate(is_intro = `Preparatory Courses` %>% str_detect("^...10")) %>%
  mutate(weight = weight * (1 + is_intro)) %>%

@@

  # aggregate prep_score
  group_by(target, `Preparatory Courses`) %>%
  summarize(prep_score = sum(prep_score)) %>%
